---
jupyter:
  jupytext:
    formats: ipynb,R:percent,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.2'
      jupytext_version: 1.8.0
  kernelspec:
    display_name: R
    language: R
    name: ir
---

# Week 2 Exercise

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(tidyverse))
cces <- suppressMessages(drop_na(read_csv("cces_sample_coursera.csv")))
```

Your objective is to replicate these figures, created using the Cooperative
Congressional Election Study data. These figures are similar to those we
completed in the lecture videos.

### Put your name here: Marcio Woitek

## Exercise 1

Hints:

* For the x-axis, use the variable `ideo5`.
* Make sure you recode the data for the `ideo5` variable to generate the
  correct names for the x-axis. You will want to consult the codebook.
* Use the fill aesthetic to have R fill in the bars. You do not need to set the
  colors manually.
* Use `guides()` to drop the legend.
* Make sure the axis labels and figure title are correct.

```{r exercise1, echo=FALSE}

```

## Exercise 2

Hints:

* For the x-axis, use the variable `pew_religimp`.
* Make sure you recode the data for the `pew_religimp` variable to generate the
  correct labels for the x-axis. You will want to consult the codebook.
* Rename the column for ideology to make sure the first letter is upper-case
  (to make the legend appear correctly).
* Use the fill aesthetic to have R fill in the bars. You do not need to set the
  colors manually.
* Make sure the axis labels and figure title are correct.

```{r exercise2, echo=FALSE}

```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.
* Create a tibble/data frame with three columns: Semester, Student, and Grade.
* There should be six semesters and three students (Amanda, Betty, and Carol).
* Create grades for the students using the `runif()` command, with values
  between 80 and 100. Hint: you'll need 18 grades total.

```{r exercise3, echo=FALSE}

```
